manuscript

### 2018-12-21 manuscript/manuscript.Rmd
re-structre hemoglobin folder
add massspretrum results

## Results and Discussion

@@

>>>>

## Results

\and Discussion

@@

### Hemoglobin evolution
Remarkably siboglinid Hbs are able to bind oxygen and sulfide simultaneously and reversibly at two different sites. To avoid the toxic effects of sulfide while supplying it to their chemoautotrophic endosymbionts, siboglinds possesses a multihemoglobin system with three different extracellular hemoglobins (Hbs; V1, V2, and C1): two dissolved in the vascular blood, V1 and V2, and one in the coelomic fluid, C1 [@arp1981blood, @zal1996multi]. Siboglinid Hbs consist of four heme-containing chains (A1, A2, B1, B2) and four linker chains (L1-L4).  Sulfur-binding capabilities are hypothesized to be due to free cysteine residues at key positions in Hbs, especially in the A2 and B2 chains. V1 Hb can form persulfide groups on its linker chains, a mechanism that can account for the higher sulfide-binding potential of this Hb [@zal1997primary]. Moreover, part of the H2S binding affinity has also been suggested to be mediated by the zinc moieties bound to amino acid residues at the interface between pairs of A2 chains in *Riftia* [@flores2005sulfide].
